Investigation of Limited Detection Schemes for Light Scattering of Optically Trapped Asymmetric Particles

### 2022-12-21 Manuscript_rev2-LL.tex
more updates

The inverse mapping from the scaled measured signal to a particular
reference orientation of the dimer was fit using a multi-layer
perceptron neural network with four hidden layers, each with 100
neurons logistic activation function.  This was implemented in Python
using the scikit-learn \cite{Pedregosa_etal_2011} library.
%to build a neural network for
%identifying the dimer's orientation from its light scattering
%signal.
The neural network was trained using the stochastic optimizer Adam
\cite{Kingma_Ba_014} on a data set that was generated by randomly
choosing $10^4$ orientations and calculating the corresponding scaled
signals from light scattering.
%
%
%and then having the network estimate the probability of the
%signal coming from our dimer in that corresponding reference
%orientation.  After making its estimation the network's loss function
%was evaluated and used to improve the estimation, we trained the
%network until the improvement in the loss function was less than
%$10^{-4}$.

@@

A key assumption of our neural network is that the scattering signal we detect has no uncertainty associated with it; in reality it is guaranteed that the signals we detect will have an inherent amount of measurement uncertainty. To demonstrate the impact of measurement uncertainty on our models performance we introduced a Gaussian noise to our measured signal.
\begin{align}
	I(\hat{\bf s}) = I(\hat{\bf s}) \pm \eta I(\hat{\bf s})
\end{align}
Where $\eta$ is the percentage error associated with our measurement. We ran our model while varying the value of $\epsilon$, Figure~\ref{fig:epsilon} shows the performance of the method with a selection of angles $15^{\circ}$, $55^{\circ}$, $90^{\circ}$ and the vertical detector at $75^{\circ}$, with $\beta$ set to $1$:

@@

As seen from Figure~\ref{fig:beta} $\beta$ helps to significantly reduce the random fluctuations in our model, eventually $\beta$ will begin to over correct our estimation. The exact value of $\beta$ that will best optimise our performance varies based on the expected signal error, therefore we can use it as variable for fine tuning our results to suit our expected signal error.

In future, we want to investigate the possibility of extending our prior $p(\hat{\bf n})$ so we account for not just the change in orientation after one time step but after 'n' time steps to investigate the auto correlation function of our dimer's motion.

>>>>

The inverse mapping from the scaled measured signal to a particular
reference orientation of the dimer was fit using a multi-layer
perceptron neural network with four hidden layers, each with 100
neurons logistic activation function.  This was implemented in Python
using the scikit-learn \cite{Pedregosa_etal_2011} library.
%to build a neural network for
%identifying the dimer's orientation from its light scattering
%signal.
The neural network was trained using the stochastic optimizer Adam
\cite{Kingma_Ba_2014} on a data set that was generated by randomly
choosing $10^4$ orientations and calculating the corresponding scaled
signals from light scattering.
%
%
%and then having the network estimate the probability of the
%signal coming from our dimer in that corresponding reference
%orientation.  After making its estimation the network's loss function
%was evaluated and used to improve the estimation, we trained the
%network until the improvement in the loss function was less than
%$10^{-4}$.

@@

A key assumption of our neural network is that the scattering signal we detect has no uncertainty associated with it; in reality it is guaranteed that the signals we detect will have an inherent amount of measurement uncertainty. To demonstrate the impact of measurement uncertainty on our models performance we introduced a Gaussian noise to our measured signal.
\begin{align}
	I(\hat{\bf s}) = I(\hat{\bf s}) \pm \eta I(\hat{\bf s})
\end{align}
where $\eta$ is the percentage uncertainty associated with the light
scattering measurement.  We tested the method for varying values of
$\eta$.  Figure~\ref{fig:epsilon} shows the performance of the method
with a selection of angles $15^{\circ}$, $55^{\circ}$, $90^{\circ}$
and the vertical detector at $75^{\circ}$, with $\beta=1$:

@@

As seen from Figure~\ref{fig:beta} $\beta$ helps to significantly
reduce the random fluctuations in our model, eventually $\beta$ will
begin to over correct our estimation.  The value of $\beta$ that will
best optimise our performance varies based on the expected signal
error, therefore we can use it as variable for fine tuning our results
to suit our expected signal error.

In future, we plan to investigate the possibility of extending our
prior $p(\hat{\bf n})$ so we account for not just the change in
orientation after one time step but after 'n' time steps to
investigate the auto correlation function of the dimer's motion.
